\documentclass[•]{article}
\usepackage{graphicx}
\usepackage{float}


\begin{document}
\title{VLSI Week 1}
\maketitle

\tableofcontents
\newpage

\section{P and N Type Silicon}
P type silicon involves doping the neutral silicon with negatively charged atoms, the introduced atoms require an electron from one of the surounding silicon atoms. This makes the silicon atom positively charged, creating a mobile positive charge, these are referred to as "holes". Holes move around through stealing their electron from surrounding silicon atoms. \\

The alternative type of doping is referred to as N-type, in which a negatively charged atom is doped in the silicon, this causes one of the surounding silicon atoms to accept an aditional electron, and become negatively charged. This electron can then be passed around the silicon substrate in order to create charge flow.

\section{Diode Design}
Diodes are created using a junction between p and n type silicon. The current is biased in such a way that it can only flow in one direction, from the p to the n junction.

\section{Transistor Design}
The design of transistors involves exploiting the mobile charge carriers of the doped silicon using an electric field to create a channel through which charge can flow. \\

NMOS transistors are built using two section of n-type silicon embedded in a well of p-type silicon. There space between the two section of n-type is referred to as the channel. The channel is in contact with a $SiO^2$ material which is impermeable to charge flow, the other side of the $SiO^2$ is plated with a conductor and referred to as the gate. Charge is deposited on the gate which generates an electric field, drawing holes upward, in order to create a channel through which charge may flow.

\section{Transistor Level Design of Digital Components}
\subsection{Inverter}
\subsection{NAND}
\subsection{NOR}
\subsection{Multi Input NAND}
\subsection{TriState Buffers}
\subsection{Multiplexers}
\subsection{Latches}
\subsection{Flip Flops}

\section{Physical Layout Level Design}

\section{Fabrication Process}





\end{document}